IEEE: artikel

### 2015-04-03 Thesisfollowup/IEEE.tex
IEEE artikel aangevuld

\documentclass[a4paper, 11pt]{article}
\setlength{\topmargin}{-.5in}
\setlength{\textheight}{9in}
\setlength{\oddsidemargin}{.100in}
\setlength{\textwidth}{6.25in}
\usepackage [dutch] {babel}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{listings}
\usepackage{color}
\usepackage{soul}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{parskip}

@@

 Not so long ago we discovered some high profile targeted attacks and the NSA who infiltrated in a lot of systems without anyone noticing it. This means that even the most secure company can still be compromised without even noticing it. Such an attack can gain access to vulnerable data, credentials, cryptographic keys and many more. APT's are..

 The problem that we want to address in this article is how to react as a defender if our network system can be compromised by an attacker in a stealthy way. A research group at the RSA proposed a game to model the scenario where the compromising the system is done stealthy and not immediately noticed by the system manager. In this FlipIt game we have 2 players, the attacker and the defender, and a shared resource.
 Both players can gain at any time control of the shared resource, but this will always happen in a secretly manner. None of the players can observe who is in control of the resource. Every unit of time that a player is in control it gets utility. A player can 'flip' a resource which means that he is taking control over the resource. Each time the player flips the resource it has to pay a fixed cost.
 In this paper we want to model the problem of a corporte network that is under attack daily by virusses and worms. To do so we have to adapt the basic FlipIt game. Instead of one shared resource we have multiple resources that represent the nodes or devices in a corporate network. Each of these nodes are connected to other nodes by a graph. \comment{email systeem }.

@@

 Now we know how we can model the spreading of the virus. If we want to set-up a gain function we have to know how ling it takes for the virus to compromise the whole system. This will be equal to the shortest path from the start infected node to the node that is the furthest away from this node. With this information we can calculate after how many steps this node is infected through our matrix calculation. We will end up with kind of a delayed FlipIT
\end{document}

>>>>

\documentclass[a4paper, 11pt]{article}
\setlength{\topmargin}{-.5in}
\setlength{\textheight}{9in}
\setlength{\oddsidemargin}{.100in}
\setlength{\textwidth}{6.25in}
\usepackage [dutch] {babel}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{listings}
\usepackage{color}
\usepackage{soul}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{multicol}

@@

 Not so long ago we discovered some high profile targeted attacks that infiltrated in a lot of systems without anyone noticing it. Belgacom [] has been the victim of a cyber security attack that has been uncovered for almost 2 years. The communication infrastructure of the Telecom company was infected with highly sophisticated malware making it possible to eavesdrop remotely. This means that even the most secure company can still be compromised without even noticing it. Such an attack can gain access to vulnerable data, credentials, cryptographic keys and many more. These kind of attacks that target organisations in a stealthy way and stay undetected for a long period are called APT (Advanced Persistent Threats).

\comment{uitleggen waarom we gametheorie gaan gebruiken om het spel te modelleren}
 The problem that we want to address in this article is how to react as a defender if our network system can be compromised by an attacker in a stealthy way. A research group at the RSA proposed a game to model the scenario where compromising the system is done stealthy and not immediately noticed by the system manager. In this FlipIt [1] game we have 2 players, the attacker and the defender, and a shared resource.
 Both players can gain at any time control of the shared resource, but this will always happen in a secretly manner. None of the players can observe who is in control of the resource. Every unit of time that a player is in control it gets utility. A player can 'flip' a resource which means that he is taking control over the resource. Each time the player flips the resource it has to pay a fixed cost.
 In this paper we want to model the problem of a corporate network that is under attack daily by viruses and worms. To do so we have to adapt the basic FlipIt game. Instead of one shared resource we have multiple resources that represent the nodes or devices in a corporate network. Each of these nodes are connected to other nodes by a graph.  \comment{email systeem }.

@@

 Now we know how we can model the spreading of the virus. If we want to set-up a gain function we have to know how ling it takes for the virus to compromise the whole system. This will be equal to the shortest path from the start infected node to the node that is the furthest away from this node. With this information we can calculate after how many steps this node is infected through our matrix calculation. We will end up with kind of a delayed FlipIT

\section{References}
\begin{itemize}
\item \textit{FlipIt: Game of stealthy takeovers}
\end{itemize}
\end{document}
